---
output: 
  rmdformats::downcute
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

source(paste0(getwd(),"/netrezerv_en.R"))

zaman <- tdt[5]$time

zaman1 <- tdt[tdt[time == zaman, which = T] - 1]$time

ilkk <- as.Date("2021-01-01")

source(paste0(getwd(),"/graphs_en.R"))

```


## CBRT Balance Sheet

<div style="float: left;"><a href=TCMB_TR_2021-03-12.html>TR</a></div>
<div style="float: right;"><a href=arsiv.html>Archive</a></div>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
DT::datatable(
  yutk,options = list(dom = 't' ), 
  caption = paste0('CBRT Balance Sheet Dated ', zaman)
)
```


`r paste0(" CBRT's net reserves ",
ifelse(sign((tdt[time == zaman]$netr) - (tdt[time == zaman1]$netr)) == 1, paste0(" increased "), paste0(" decreased ")),
" by ",
paste0(abs(round((tdt[time == zaman]$netr) - (tdt[time == zaman1]$netr), 2)))," Million Dollars ",
" compared to last week, and ",
ifelse(sign((tdt[time == zaman]$netr) - (tdt[time == "2021-01-01"]$netr)) == 1, paste0(" expanded "), paste0(" declined ")),
" by ",
paste0(abs(round((tdt[time == zaman]$netr) - (tdt[time == "2021-01-01"]$netr), 2))),
" Million Dollars ",
" compared to the new year. ",
" Net reserves excluding swap ",
ifelse(sign((tdt[time == zaman]$shnetr) - (tdt[time == zaman1]$shnetr)) == 1, paste0(" rise "), paste0(" fell ")),
" by ",
paste0(abs(round((tdt[time == zaman]$shnetr) - (tdt[time == zaman1]$shnetr), 2))), 
" Million Dollars ",
" compared to previous week, and ",
ifelse(sign((tdt[time == zaman]$shnetr) - (tdt[time == "2021-01-01"]$shnetr)) == 1, paste0(" raised "), paste0(" dropped ")),
" by ",
paste0(abs(round((tdt[time == zaman]$shnetr) - (tdt[time == "2021-01-01"]$shnetr), 2))), 
" Million Dollars ",
" compared to the new year. " 
       ) `
       
`r paste0(" Net gold reserves ",
       ifelse(sign((tdt[time == zaman]$nar) - (tdt[time == zaman1]$nar)) == 1, paste0("rise"), paste0("decline")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$nar) - (tdt[time == zaman1]$nar), 2))), 
       " Million Dollars ",
       " since last week and ",
       ifelse(sign((tdt[time == zaman]$nar) - (tdt[time == "2021-01-01"]$nar)) == 1, paste0(" gain "), paste0(" loss ")),
       paste0(abs(round((tdt[time == zaman]$nar) - (tdt[time == "2021-01-01"]$nar), 2))), 
       " Million Dollars ",
       " since the new year and reached to ",
       paste0(round((tdt[time == zaman]$nar), 2)), " Million Dollars. "
       
) `
`r paste0(" Net foreign exchange reserves ",
       ifelse(sign((tdt[time == zaman]$ndr) - (tdt[time == zaman1]$ndr)) == 1, paste0(" increased "), paste0(" decreased ")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$ndr) - (tdt[time == zaman1]$ndr), 2))), 
       " Million Dollars ",
       " compared to previous week and ",
       ifelse(sign((tdt[time == zaman]$ndr) - (tdt[time == "2021-01-01"]$ndr)) == 1, paste0(" rise "), paste0(" fell ")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$ndr) - (tdt[time == "2021-01-01"]$ndr), 2))), 
       " Million Dollars ",
       " and reached to ",
       paste0(round((tdt[time == zaman]$ndr), 2)), " Million Dollars. "
       
) `

`r paste0(" Since last week, net gold reserves excluding swap ",
       ifelse(sign((tdt[time ==zaman]$shnar) - (tdt[time == zaman1]$shnar)) == 1, paste0(" raised "), paste0(" dropped ")),
       " by ",
       paste0(abs(round((tdt[time ==zaman]$shnar) - (tdt[time == zaman1]$shnar), 2))), 
       " Million Dollars ",
       " and reached to ",
       paste0(round(tdt[time ==zaman]$shnar, 2)), " Million Dollars. ",
       " In addition, net foreign exchange reserves excluding swap ",
       ifelse(sign((tdt[time == zaman]$shndr) - (tdt[time == zaman1]$shndr)) == 1, paste0(" expanded "), paste0(" declined ")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$shndr) - (tdt[time == zaman1]$shndr), 2))),
       " Million Dollars ",
       " and reached to ",
       paste0(round((tdt[time == zaman]$shndr), 2)), " Million Dollars. "
) `

`r paste0(" Total liabilities (including balance sheet and off-balance sheet) ",
       ifelse(sign((tdt[time == zaman]$ty) - (tdt[time == zaman1]$ty)) == 1, paste0(" increased "), paste0(" decreased ")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$ty) - (tdt[time == zaman1]$ty), 2))), 
       " Million Dollars ",
       " since the last week. ",
       " Also, it ",
       ifelse(sign((tdt[time == zaman]$ty) - (tdt[time == "2021-01-01"]$ty)) == 1, paste0(" rise "), paste0(" fell ")),
       " by ",
       paste0(abs(round((tdt[time == zaman]$ty) - (tdt[time == "2021-01-01"]$ty), 2))), 
       " Million Dollars ",
       " and reached to ",
       paste0(round((tdt[time == zaman]$ty)/1000, 2)), " Billion Dollars, ",
       " compared to the new year. "
       
) `

`r paste0(" The ratio of off-balance sheet liabilities to gross reserves is % ", round(tdt[time == zaman]$bdybro, 2), " . ")`

### CBRT Reserves and Liabilities

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="110%"}
fig
```

### Net Reserves Position

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="110%"}
nr
```

### Net Reserves (excluding Swap) Position

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="110%"}
snr
```


### Magnitude of Off-Balance Sheet Transactions

```{r, echo=FALSE, warning=FALSE, message=FALSE, out.width="110%"}
zama
tgr
a
b
c
d
e
f
g
sub1
sub2
sub3
sub4
```

## Detailed Table

```{r, echo=FALSE, warning=FALSE, message=FALSE}
DT::datatable(
  det_tab,options = list(dom = 't',
                         pageLength = 33), 
  caption = paste0('Detailed CBRT Balance Sheet Dated ', zaman)
) %>% formatStyle(
  'Accounts',
  target = 'row',
  backgroundColor = styleEqual(c("Gross FX Reserves" , #1
"Total Cash and Deposit" , #2
"Securities" , #3
"Gross Gold Reserves" , #4
"Gross SDR Reserves" , #5
"Total Gross Reserves" , #6 
"Banking Sector Balance Sheet" , #7
"Required Reserves" , #8
"Required Reserves - FX" , #9
"Required Reserves - Gold" , #10
"Domestic Banks" , #11
"Domestic Banks - Cash" , #12
"Domestic Banks - Collateral" , #13
"Domestic Banks - Gold" , #14
"CBRT's Liabilities to Foreign Banks" , #15
"SDR Liabilities" , #16
"Other Deposits" , #17
"Balance Sheet FX Liabilities" , #18
"Balance Sheet Gold Liabilities" , #19
"Balance Sheet Liabilities" , #20
"Domestic Banks - Swap" , #21
"Domestic Banks - Swap - FX" , #22
"Domestic Banks - Swap - Gold" , #23
"Foreign Central Banks - Swap" , #24
"Off Balance Sheet FX Liabilities" , #25
"Off Balance Sheet Gold Liabilities" , #26
"Off Balance Sheet Liabilities" , #27
"Net FX Reserves" , #28
"Net Gold Reserves" , #29
"Net Reserves" , #30
"Net FX Reserves (excluding Swap)" , #31
"Net Gold Reserves (excluding Swap)" ,  #32
"Net Reserves (excluding Swap)"  #33
), 
c("#808080" , #1
"#606060" , #2
"#606060" , #3
"#808080" , #4
"#808080", #5
"#B0B0B0" , #6 
"#808080" , #7
"#606060" , #8
"#404040" , #9
"#404040" , #10
"#606060" , #11
"#404040" , #12
"#404040" , #13
"#404040" , #14
"#808080" , #15
"#808080" , #16
"#808080", #17
"#A0A0A0" , #18
"#A0A0A0" , #19
"#B0B0B0" , #20
"#808080" , #21
"#606060" , #22
"#606060" , #23
"#808080" , #24
"#A0A0A0" , #25
"#A0A0A0" , #26
"#B0B0B0" , #27
"#A0A0A0" , #28
"#A0A0A0" , #29
"#B0B0B0" , #30
"#A0A0A0" , #31
"#A0A0A0" ,  #32
"#B0B0B0"  #33
 ))
)
```

## Methodology


<a href="#">Go to top of page</a>